Supporting Information

### 2018-03-13 SupportingInformation.Rmd
adding line in Yaml chunk

output: 
  pdf_document:
    number_sections: yes
    keep_tex: yes
    fig_caption: yes
tables: True

@@

<!--
```{r, echo=F}
options(knitr.table.format = "html")
```
-->

>>>>

output: 
  pdf_document:
    number_sections: yes
    keep_tex: yes
    fig_caption: yes
tables: True
link-citations: true

@@

<!--
```{r, echo=F}
options(knitr.table.format = "html")

```
-->
